\documentclass[12pt]{article}
\usepackage{setspace}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
%\usepackage{mathabx}
\pagestyle{empty}

\textwidth 6.5in
\hoffset=-.65in
\textheight=9.5in
\voffset=-1.in

\begin{document}

\noindent MATH 307 \\
Assignment \#14 \\
Due any time, any year \\

For each problem, include the statement of the problem. Leave a blank line.  At the beginning of the next line, write \textbf{Solution} or \textbf{Proof} -- as appropriate.

\begin{enumerate}
\item Suppose $T \in \mathcal{L}(\mathbf{C}^4)$ is such that the eigenvalues of $T$ are 3, 5 8.  Prove that $(T-3I)^2 (T-5I)^2 (T-8I)^2 = 0$.

\item Give an example of an operator on $\mathbf{C}^4$ whose characteristic polynomial equals \\ $(z-1)(z-5)^3$ and whose minimal polynomial equals $(z-1)(z-5)^2$.

\item Suppose $V$ is a complex vector space.  Suppose $P \in \mathcal{L}(V)$ is such that $P^2=P$.  Prove that the characteristic polynomial of $P$ is $z^m(1-z)^n$, where $m = \dim \null P$ and $n = \dim \text{range }P$.

\item Suppose $T \in \mathcal{L}(V)$ has minimal polynomial $2-3z+z^2-5z^3+7z^4+6z^5$. Find the minimal polynomial of $T^{-1}$.

\item Suppose $T \in \mathcal{L}(V)$ is invertible. Prove that there exists a polynomial $p \in \mathcal{P}(\mathbf{F})$ such that $T^{-1} = p(T)$.

\item Suppose $V$ is an inner product space and $T \in \mathcal{L}(V)$ is normal. Prove that the minimal polynomial of $T$ has no repeated zeros.

\item Suppose $N \in \mathcal{L}(V)$ is nilpotent. Prove that the minimal polynomial of $N$ is $z^{m+1}$, where $m$ is the length of the longest consecutive string of $1$’s that appears on the line directly above the diagonal in the matrix of $N$ with respect to any Jordan basis for $N$.

\item Suppose $T \in \mathcal{L}(V)$ and $v_1 , \ldots , v_n$ is a basis of $V$ that is a Jordan basis for $T$. Describe the matrix of $T^2$ with respect to this basis.

\item Suppose $p , q \in \mathcal{P}(\mathbf{C})$ are monic polynomials with the same zeros and $q$ is a polynomial multiple of $p$. Prove that there exists $T \in \mathcal{L}(\mathbf{C}^{\deg q})$ such that the characteristic polynomial of $T$ is $q$ and the minimal polynomial of $T$ is $p$.

\end{enumerate}

\end{document} 