\documentclass[12pt]{article}
\usepackage{setspace}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
%\usepackage{mathabx}
\pagestyle{empty}

\textwidth 6.5in
\hoffset=-.65in
\textheight=9.5in
\voffset=-1.in

\begin{document}

\noindent MATH 307 \\
Assignment \#5 \\  %3.D, 3.E 
Due Friday, February 18, 2022 \\

For each problem, include the statement of the problem. Leave a blank line.  At the beginning of the next line, write \textbf{Solution} or \textbf{Proof} -- as appropriate.

\begin{enumerate}
\item Let $V$ be a finite-dimensional vector space and let $A,B,C,D \in \mathcal{L}(V)$.  Assume that $A+B$ and $A-B$ are invertible.  Show that there exist $X,Y$ so that
    \begin{align*}
    AX + BY &= C \\
    BX + AY &= D.
    \end{align*}

\item Show that if $A \in \mathcal{L}(V)$ satisfying $A^2 -A+I=0$, then $A$ is invertible.

\item Assume $V$ is a finite-dimensional vector space with $S,T,U \in \mathcal{L}(V)$.  Show that if $STU=I$ then $T$ is invertible and $T^{-1}= US$

\item Let $V$ be a 2-dimensional vector space and let $A \in \mathcal{L}(V)$ be invertible.  Show that there is a polynomial $p$ so that $A^{-1} = p(A)$.

\item Let$V$ and $W$ be finite-dimensional vector spaces. Fix $v \in V$. Define
    \[
        E = \{ T \in \mathcal{L}(V,W) : Tv=0 \}.
    \]
    \begin{enumerate}
    \item Show that $E$ is a subspace of $\mathcal{L}(V,W)$.
    \item Suppose $v \ne 0$.  What is $\dim E$?
    \end{enumerate}

\item  Let $V= \mathbf{R}^{2,2}$ be the vector space of $2 \times 2$ matrices with the usual addition and scalar multiplication of matrices.  Let $W = \mathcal{P}_3(\mathbf{R})$ be the vector space of polynomials of degree less than or equal to three.  Prove that $V$ and $W$ are isomorphic vector spaces.

\item Let $V$ be a real vector space.  $V^4 = V \times V \times V \times V$.  Prove that $V^4$ and $\mathcal{L}(\mathbf{R}^4, V)$ are isomorphic vector spaces.

\end{enumerate}

\end{document} 