\documentclass[12pt]{article}
\usepackage{setspace}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
%\usepackage{mathabx}
\pagestyle{empty}

\textwidth 6.5in
\hoffset=-.65in
\textheight=9.5in
\voffset=-1.in

\begin{document}

\noindent MATH 307 \\
Assignment \#10 \\  % 7.C, 7.D
Due Friday, April 1, 2022 \\$\;\;$ CORRECTION: Removed a duplicate problem \#1: 29Mar2022.\\


For each problem, include the statement of the problem. Leave a blank line.  At the beginning of the next line, write \textbf{Solution} or \textbf{Proof} -- as appropriate.

\begin{enumerate}
\item Suppose that $T$ is a normal operator on $V$ and that 3 and 4 are eigenvalues of $T$.  Prove that there exists a vector $v \in V$ such that $\|v\| = \sqrt{2}$ and $\|Tv\| = 5$.

\item \begin{enumerate}
        \item Suppose that $T$ is a self-adjoint operator on a finite-dimensional inner product space and that 2 and 3 are the only eigenvalues of $T$.  Prove that $T^2-5T+6I=0$.
        \item Give an example of an operator $T \in \mathcal{L}(\mathbf{C}^3)$ such that 2 and 3 are the only eigenvalues of $T$ and $T^2-5T+6I \ne 0$.
        \end{enumerate}

\item  Suppose that $T$ is a normal operator on $V$.  Suppose also that $v, w \in V$ satisfy the equations
    \[
        \|v\| = \|w\| = 2, \hspace{.25in} Tv=3v, \hspace{.25in} Tw=4w.
    \]
    Show that $\|T(v+w)\| = 10$.

\item Suppose $T \in \mathcal{L}(V)$ is normal.  Prove that $\text{range }T = \text{range }T^*$.

\item
  Consider the statement: If $T \in \mathcal{L}(V)$ and there exists an orthonormal basis $e_1, \ldots , e_n$ of $V$ such that $\|Te_j\| = \|T^*e_j\|$ for each $j$, then $T$ is normal.  Show that a counterexample to the statement is given by the matrix
    $T = \left(
  \begin{array}{cc}
    0 & 1  \\
    -1 & 2  \\
  \end{array}
\right)$ with respect to the standard basis in $\mathbf{R}^2$.

\item (CST) Suppose $\mathbf{F} = \mathbf{C}$ and $T \in \mathcal{L}(V)$. Prove that $T$ is normal if and only if all pairs of eigenvectors corresponding to distinct eigenvalues of $T$ are orthogonal and
    \[
        V = E(\lambda_1,T) \oplus \cdots \oplus E(\lambda_m,T)
    \]
    where $\lambda_1 , \ldots , \lambda_m$ denote the distinct eigenvalues of $T$.

\item (CST) Prove that a normal operator on a complex inner product space is self-adjoint if and only if all its eigenvalues are real.

\item (CST) Suppose $V$ is a complex inner product space. Prove that every normal operator on $V$ has a square root. (An operator $S \in \mathcal{L}(V)$ is called a \emph{square root} of S$ \in \mathcal{L}(V)$ if $S^2 = T$.)

\end{enumerate}

\end{document}

\left(
  \begin{array}{ccc}
     &  &  \\
     &  &  \\
     &  &  \\
  \end{array}
\right)
