\documentclass[12pt]{article}
\usepackage{setspace}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
%\usepackage{mathabx}
\pagestyle{empty}

\textwidth 6.5in
\hoffset=-.65in
\textheight=9.5in
\voffset=-1.in

\begin{document}

\noindent MATH 307 \\
Assignment \#9 \\ % 7.A, 7.B
Due Friday, March 25, 2022 \\

For each problem, include the statement of the problem. Leave a blank line.  At the beginning of the next line, write \textbf{Solution} or \textbf{Proof} -- as appropriate.

\begin{enumerate}
\item Suppose $V$ is finite-dimensional and $P \in \mathcal{L}(V)$ is such that (1) $P^2 = P$ and (2) every vector in $\text{null } P$ is orthogonal to every vector in $\text{range }P$. Prove that there exists a subspace $U$ of $V$ such that $P = P_U$.\\
    Hint:  For $v \in V$, write $v = Pv + (v-Pv)$.

\item Suppose $V$ is finite-dimensional, $T \in \mathcal{L}(V)$ and $U$ is a subspace of $V$.  Prove that $U$ is invariant under $T$ if and only if $P_UTP_U = TP_U$.

\item In $\mathbf{R}^4$, let
    \[
        U = \text{span}\left((0,0,1,1) , (1,2,1,1) \right).
    \]
    Find $u \in U$ such that $\|u - (1,3,5,4) \|$ is as small as possible.
    
\item  Assume $T \in \mathcal{L}(V)$ for a complex vector space $V$.  Prove that $T$ is self-adjoint if and only if all eigenvalues for $T$ are real.

\item If $T \in \mathcal{L}(V)$ is self-adjoint and if $T^2v = 0$, then $Tv=0$

\item Suppose $T \in \mathcal{L}(V,W)$. Prove that
    \begin{enumerate}
    \item $T$ is injective if and only if $T^*$ is surjective.
    \item $T$ is surjective if and only if $T^*$ is injective.
    \end{enumerate}

\item Suppose $S,T \in \mathcal{L}(V)$ are self-adjoint.  Prove that $ST$ is self-adjoint if and only if $ST = TS$.

\item Suppose $T \in \mathcal{L}(V)$ is such that $P^2 = P$.  Prove that there is a subspace $U$ of $V$ such that $P = P_U$ if and only if $P$ is self-adjoint.

\end{enumerate}

\end{document} 