\documentclass[12pt]{article}
\usepackage{setspace}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
%\usepackage{mathabx}
\pagestyle{empty}

\textwidth 6.5in
\hoffset=-.65in
\textheight=9.5in
\voffset=-1.in

\begin{document}

\noindent MATH 307 \\
Assignment \#2 \\  % 2.A
Due Friday, January 28, 2022 \\

For each problem, include the statement of the problem. Leave a blank line.  At the beginning of the next line, write \textbf{Solution} or \textbf{Proof} -- as appropriate.

\begin{enumerate}
\item Label the following statements as being true or false.
Provide some justification from the text for your label.
    \begin{enumerate}
        \item  If $V$ is a vector space and $W$ is a subset of $V$ that is a vector space, then $W$ is a subspace of $V$.
        \item The empty set is a subspace of every vector space.
        \item If $V$ is a vector space other than the zero vector space $\{0\}$, then $V$ contains a subspace $W$ such that $W \ne V$.
        \item The intersection of any two subsets of $V$ is a subspace of $V$.
    \end{enumerate}

\item  Prove that the intersection of two subspaces $U$ and $W$ of a vector space $V$ is a subspace of $V$.

\item  Prove that the union of two subspaces  $U$ and $W$ of a vector space $V$ is a subspace of $V$ if and only if one of of the subspaces is contained in the other.

\item Let $V$ be the vector space of $2 \times 2$ matrices with the usual operation of addition and scalar multiplication as seen in MTH 207.  (We are \emph{not} considering multiplication of matrices in this exercise.)\\
    Let $W_1$ be the set of matrices in $V$ of the form
    $\left[
      \begin{array}{cc}
        x & -x \\
        y & z \\
      \end{array}
    \right]$ and let $W_2$ be the set of matrices in $V$ of the form
    $\left[
      \begin{array}{cc}
        a & b \\
        -a & c \\
      \end{array}
      \right]$.
      \begin{enumerate}
      \item Prove that $W_1$ and $W_2$ are subspaces of $V$.
      \item Describe the subspace $W_1 \cap W_2$.
      \item Show that the subspace $W_1 + W_2$ is all of $V$.
      \end{enumerate}

\item  Prove or give a counterexample:  if $U_1, U_2,W$ are subspaces of the vector space $V$ such that $V = U_1 \oplus W$ and $V = U_2 \oplus W$, then $U_1 = U_2$.

\item  Let $V = \mathbf{R}^3$ -- the usual 3D space from Calc III.  Let $U$ be the $x$-axis.  Define $W$ to be the subspace spanned by $(1,0,1)$.  Show that the usual $xz$-plane is the direct sum $U \oplus W$.

\item  Suppose that the vectors $v_1, v_2, v_3, v_4$ span the vector space $V$.  Show that the vectors $v_1-v_2, v_1+v_2, v_3+v_4, v_4$ also span $V$.

\end{enumerate}

\end{document} 